Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
abstract + intro

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to reassess the effects of combining \ds{} with \sfl{}.  With this
combination, components that are often involved in failing but seldom
in passing test runs could be located and their suspiciousness
reduced. Results show that the \ds{}-\sfl{} combination, coined as
Tandem-SL, improves the diagnostic accuracy up to $73.7\%$
(\avgImprov\ on average). Furthermore, results indicate that the risk
of missing faulty statements, which is a \ds{}'s key limitation, is not
high---~\ds{} misses faulty statements in $9\%$\comments{($23$
  misses)} of the $\numFaults{}$ cases. To sum, we found that the
\ds{}-\sfl{} combination was practical and effective and encourage new
\sfl{} techniques to be evaluated against that optimization.
\end{abstract}

@@

The contributions of this work are: 1)~an empirical study, using
real-world applications and bugs, on the combination of \ds{} and
\sfl{} for bug localization of \emph{Java} faulty programs and 2)~a
tool, dubbed \comb{}, implementing the \ds{}-\sfl{} combination. The
tool as well as a replication package will be available once
double-blind requirements are lifted.

>>>>

\begin{abstract}
Several approaches have been proposed to reduce debugging costs through
automated software fault diagnosis.  Dynamic Slicing (\ds{}) and Spectrum-based
Fault Localization (\sfl{}) are popular fault diagnosis techniques and normally
seen as complementary. This paper reports on a comprehensive
study\comments{--using \numFaults{} documented software faults from a credible
dataset--} to reassess the effects of combining \ds{} with \sfl{}.  With this
combination, components that are often involved in failing but seldom in passing
test runs could be located and their suspiciousness reduced. Results show that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic
accuracy up to $73.7\%$ (\avgImprov\ on average). Furthermore, results indicate
that the risk of missing faulty statements, which is a \ds{}'s key limitation,
is not high~---~\ds{} misses faulty statements in $9\%$\comments{($23$ misses)}
of the $\numFaults{}$ cases. To sum, we found that the \ds{}-\sfl{} combination
was practical and effective and encourage new \sfl{} techniques to be evaluated
against that optimization.
\end{abstract}

@@

The contributions of this work are:
\begin{itemize}
 \item[1)]~an empirical study, using
real-world applications and bugs, on the combination of \ds{} and
\sfl{} for bug localization of \emph{Java} faulty programs and
\item[2)]~a
tool, dubbed \comb{}, implementing the \ds{}-\sfl{} combination.
\end{itemize}
The
tool as well as a replication package will be available once
double-blind requirements are lifted.
